Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex

ashi TODO

Let's say the coarse operator runs in time $t$, and the fine operator runs in
time $Q \cdot t$. Assume we have $N$ processors and we perform $k$ correction
steps. Then, the runtime of Parareal is, assuming negligible setup and
aggregation time,

@@

@@

Varying Iterations:

Varying Quality Factor:
We define the quality factor in this case for how many times smaller the Euler method used for $g_{fine}$ is compared to the Euler method used for $g_{\Delta t}$

@@

Now with 3 different parallel implementations, two in time wiht the parareal, one in space,  we compare across TODO WESLSEY

>>>>

We look to compute a theoretical maximum speedup enabled by the nature of the Parareal algorithm.  As this is a tradeoff between error (with parameter k being the number of iterations of corrections, each which takes another cycle of $g_{\Delta t}$, we seek to express the tradeoff as a function of the quality factor, $Q$, the number of iterations, $k$ and the number of processors $n$.  Our quality factor is defined as the multiplicative factor of additional time necessary to

Then, the runtime of Parareal is, assuming negligible setup and
aggregation time,

@@

\subsection{Expectations}
TODO WESLEY
\subsection{General Remarks about Resuts}
One of the TODO WESEY

@@

Varying Iterations:
]
Varying Quality Factor:
We define the quality factor in this case for how many times smaller the Euler method used for $g_{fine}$ is compared to the Euler method used for $g_{\Delta t}$

@@

Now with 3 different parallel implementations, two in time with the parareal, one in space, we compare across the methods to see if we can make any statements about general performance of our different paradigms.
